mir\_eval

### 2014-05-01 paper/paper.tex
Beat metrics described

@@

>>>>

% MIR intends to act like humans
% Human evaluation is costly
% Metrics are used as a proxy

% Evaluation should be easy and standardized
% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, etc.
% As a result many different implementations of metrics, and implementation matters
% mir_eval as the antidote to the above

@@

\subsection{Beat Detection}

The aim of a beat detection algorithm is to report the times at which a typical human listener might tap their foot to a piece of music.  As a result, most metrics for evaluating the performance of beat tracking systems involve computing the error between the estimated beat times and some reference list of beat locations.  Many metrics additionally compare the beat sequences at different metric levels in order to deal with the ambiguity of tempo \cite{levy2011improving}.

mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The f-measure of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; Cemgil's score, which computes the sum of Gaussian errors for each beat; Goto's score, a binary score which is 1 when some specific heuristic criteria are met, McKinney's P-score, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; continuity-based scores which compute the proportion of the beat sequence which is continuously correct; and finally the information gain of the beat error histogram to a uniform distribution.
